\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim} \usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.08003pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{0.75in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% HEADING
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{{\Huge Mershab Issadien}} & \href{mailto:mershab99@gmail.com}{mershab99@gmail.com}\\
  +1416-578-5089 &\href{www.linkedin.com/in/mershab-issadien}{linkedin.com/in/mershab-issadien}\\
  {\small Toronto, Canada}
& \href{www.github.com/mershab99}{github.com/mershab99}\\
  {\small ``Any sufficiently advanced technology is indistinguishable from magic." - Arthur C. Clarke}
& \href{www.gitlab.com/mershab99}{gitlab.com/mershab99}\\
\end{tabular*}

% Programming Skills
\section{Programming Skills}
\resumeItemListStart
  \resumeItem{Languages/Databases}{: Python, Java, C\#, C++, Golang, Scala, MongoDB, PostgresSQL, InfluxDB, Redis}
  \resumeItem{APIs/Tools}{: Protobuf/gRPC, Kafka, RabbitMQ, Dapr, WebRTC, Helm, YAML, JSON, Stripe, Rook Ceph, S3, Git}
  \resumeItem{Frameworks}{: Spring Boot MVC, Dropwizard, FastAPI, Flask, Django, Maven, Gradle, Faust, Echo, Gin, SQLC, Pydantic}
  \resumeItem{IDE/OS}{: Intellij, NeoVIM, Pycharm, VS Code, RHEL 7, RHEL 8, CentOS (Rocky Linux), Ubuntu, Linux Mint, Manjaro, Proxmox, Talos Linux, Kairos}
  \resumeItem{Dev Ops}{: ArgoCD , K3s, Gitlab, Ansible, Docker, Gitlab Pipelines (CI/CD), Github Actions, Crossplane, Terraform, Prometheus}
  \resumeItem{Cloud}{: Kubernetes, AWS [AKS, RDS, SNS, Lambda), GCP (Google Cloud Platform) [GKS, Cloud Run, Google Vision API] , Azure (Microsoft) [AKS], Crossplane, VCluster, Kubevirt, OpenFunctions (Contributor)}
  \resumeItem{Soft Skills}{: Detail Oriented, Financial Technology, Market Technology, Business Requirements, Inter and intra team communication, Flexible, Team Oriented, Analytical, Systems Thinking, Customer Success}
  \resumeItem{AI/Analytics}{: Tensorflow, Pytorch, Grafana, Graylog, Datadog, Streamlit (Python)}
  \resumeItem{Cyber Security/QA Testing}{: Wireshark, K6, Locust, Metasploit, Hashcat, Aircrack-ng, Kube-Hunter, Pytest, KubeTest, Ginkgo, JUnit, J2EE}
\resumeItemListEnd

% Experience
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Nasdaq Inc.}{Toronto, ON}
    {Software Engineer, Market Technology}{September 2021 - August 2023}
    \resumeItemListStart
      \resumeItem{}
      {Wrote well crafted, unit and intergration tested, high-efficiency, high-throughput, low-memory impact Java Spring Boot microservices.}
      \resumeItem{}
      {Worked with industry-standard FIX Financial Protocol and other Nasdaq proprietary protocols.}
      \resumeItem{}
      {Worked with cross-team domain experts, business analysts, and specification writers, to debug and verify existing code paths, business functionality, and perform long term planning (AGILE EPIC Level) and Sprint forecasting.}
      \resumeItem{}
      {Increased code test coverage to 85\% and improved integration test framework to increase reliability and meet customer SLAs.}
      \resumeItem{}
      {Implemented Tailor Made Combinations (TMC's) and other key financial business logic related to the FIX protocol.}
      \resumeItem{}
      {Handled customer issues and requests from worldwide stock exchanges.}
      \resumeItem{}
      {Influenced the design of 24x7 and Snapshot Gateway Functionality and implemented in various gateways.}
      \resumeItem{}
      {Used Wireshark and performed penetration testing, as well as white-box and black-box testing and packet injection testing at the TCP level to ensure all code paths designed could not be exploited. Especially during high traffic scenarios.}
      \resumeItem{}
      {Performed load testing and integration testing to ensure compliance and limit exploits (timing or otherwise) on the system.}
      \resumeItem{}
      {Performed chaos testing to ensure resilience and uptime of system, as well as assess self healing capabilities.}
      \resumeItem{}
      {Participated in SCRUM meetings, planning, and all aspects of the Software Development Lifecycle (SDLC) within an Agile team.}
      \resumeItem{}
      {Wrote service/dev environment/onboarding documentation, Reported bugs in JIRA tickets}
      \resumeItem{}
      {Impact: Improved developer productivity (through documentation and team building), enhanced AGILE SDLC process in the team (with communication), became a subject domain expert (FIX Protocol). Shipped key business features (TMC's and 24/7). Cut releases for big clients. Improved code reliability and QA process.}
    \resumeItemListEnd

  \resumeSubheading
  {Praizl Inc. - DMZ 2021}{Toronto, ON}
  {Full-Stack Software Engineer}{July 2020 - June 2021}
    \resumeItemListStart
      \resumeItem{}
      {Contributed to startup from its inception to the DMZ Class of 2021.}
      \resumeItem{}
      {Engineered an ML recommendations engine using multiple datasets to match users to their dream homes accurately. (Developed Business's core tech)}
      \resumeItem{}
      {Provided business intelligence and user management through REST APIs using Flask and Dropwizard.}
      \resumeItem{}
      {Built an analytics framework on top of a MongoDB datalake used to process large amounts of data.}
      \resumeItem{}
      {Reduced API response time to users by 90\% by implementing an asynchronous job scheduler and in-memory caching layer using Redis.}
      \resumeItem{}
      {Performed infrastructure-level DevOps work with containerized deployments on AWS EC2.}
      \resumeItem{}
      {Achieved 80\% unit test coverage for critical algorithms.}
      \resumeItem{}
      {Collaborated in Agile teams using the Scrum methodology under the supervision of ex-Salesforce, ex-Uber, ex-Microsoft software engineers.}
      \resumeItem{}
      {Impact: Successfully bootstrapped a startup and developed production grade polyglot (multi-language) microservice based software using containerization. In addition to developing ML/data science knowledge.}
    \resumeItemListEnd

  \resumeSubheading
  {Founderbyte}{Toronto, ON}
  {Full-Stack Software Engineer}{January 2021 - June 2021}
    \resumeItemListStart
      \resumeItem{}
      {Minimized deployment costs by creating an event driven mail service using AWS Lambda and Sendgrid}
      \resumeItem{}
      {Provided business intelligence and user management through REST APIs using Flask and Dropwizard.}
      \resumeItem{}
      {Hosted client websites on DigitalOcean with custom mail service. Founderbyte.com, aquaries.co}
      \resumeItem{}
      {Built online e-commerce store with scheduling system}
      \resumeItem{}
      {Integrated scheduling widgets into existing website platforms.}
      \resumeItem{}
      {Impact: Managed a small team and business stakeholders to perform client requests.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

% Education
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Ottawa}{Ottawa, ON}
    {BSc. Honours Computer Science}{September 2017 - December 2024}
    \resumeItemListStart
      \resumeItem{Notable Courses: }{Cryptography, Networking, Data Science, Data Structures and Algorithms, Requirements Engineering, Software Engineering, Statistics, Formal Languages, Technical Report Writing}
      \resumeItem{Clubs/Projects: }{UOttawa CSME (Engineering Association), UOttawa Dota 2 B Team Captain, SemEval: AI Textual Emotion Cause-Pair Honours Project}
    \resumeItemListEnd
  \resumeSubheading
    {HRD University}{Qatar (Remote)}
    {Lean Six Sigma and RPA Dynamics}{March 2025}
  \resumeSubheading
    {Richmond Green Secondary School}{Richmond Hill, ON}
    {High School}{September 2013 - June 2017}
    \resumeItemListStart
      \resumeItem{Notable Courses: }{Engineering, Computer Science, Calculus, Advanced Functions, Physics, Chemistry, Accounting}
      \resumeItem{Clubs/Projects: }{Hour of Code, Computer Science Club Member, YRDSB QUEST 2015-2016 Project(s) member}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% Projects
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheading
  {Uottahack 4}{Ottawa, ON}
  {Team Winner - Sanitation Station Companion}{February 2021}
    \resumeItemListStart
      \resumeItem{}
      {Winner of Best Hardware Hack}
      \resumeItem{}
      {Deployed AI computer vision application using Raspberry Pi, GKS, and Google Vision API}
      \resumeItem{}
      {https://devpost.com/software/sanitation-station-companion}
      \resumeItem{}
      {Impact: Deployed a working multi tiered embedded/cloud application using Google Cloud in a Hackathon}
    \resumeItemListEnd
  \resumeSubheading
  {Ryerson DMZ Climate Hack-To-Action Hackathon}{Toronto, ON}
  {Team Hackathon Competitor - 3rd Place}{May 2016}
    \resumeItemListStart
      \resumeItem{}
      {Developed a user-focused carbon credit Android application with a SQL backend within 24 hours.}
      \resumeItem{}
      {Impact: Worked in a high stakes environment as sole tech member of a business hackathon.}
    \resumeItemListEnd
  \resumeSubheading
  {Open Source Contribution}{Toronto, ON}
  {OpenFunction}{June 2024}
    \resumeItemListStart
      \resumeItem{}
      {Exposed lower level APIs for business use cases}
      \resumeItem{}
      {Improved documentation for both developers and project consumers}
      \resumeItem{}
      {Impact: Practiced Contribution Guidelines and Documentation standards/skills.}
    \resumeItemListEnd
  \resumeSubheading
  {Open Source Contribution}{Toronto, ON}
  {Chisel Operator}{June 2024}
    \resumeItemListStart
      \resumeItem{}
      {Reported bugs with appropriate documentation.}
      \resumeItem{}
      {Communicated with maintainers to discuss bugs and features.}
      \resumeItem{}
      {Impact: Practiced Efficient Bug Reporting in Open Source Software}
    \resumeItemListEnd
  \resumeSubheading
  {Homelab}{Toronto, ON}
  {Kubernetes Based Homelab/Private Cloud}{January 2020 - Current}
    \resumeItemListStart
      \resumeItem{}
      {Built and manage my own private cloud on Kubernetes.}
      \resumeItem{}
      {Evolved from Proxmox to entirely Kubernetes GitOps (using ArgoCD) based GPU enabled private cloud.}
      \resumeItem{}
      {Cloud like experience with public IP LoadBalancer provisioning (chisel operator) and cloud storage configured with Rook Ceph.}
      \resumeItem{}
      {Built my own PaaS using VCluster, and several operators, including a DBaaS, KaaS, and SaaS}
      \resumeItem{}
      {Nested virtualization and K8s-in-K8s with managed Control Plane using Kubevirt, CAPI (Cluster API), Kamaji}
      \resumeItem{}
      {Functions as a Service provided by OpenFunction}
      \resumeItem{}
      {Impact: Perfect Sandbox to teach me modern DevOps and deployment as well as cloud automation techniques at a production grade level.}
    \resumeItemListEnd
  \resumeSubheading
  {Estatelamp}{Toronto, ON}
  {Startup - Project}{January 2024}
    \resumeItemListStart
      \resumeItem{}
      {Generated online wills for clients using Python Jinja templating.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%---------HOMELAB--------
%\section{Homelab}
%\resumeSubHeadingListStart
%  \resumeSubheading
%  {I Made a Thing}{It's a Cool Thing}{A Rad Thing}{YO}
%    \resumeItemListStart
%      \resumeItem{}
%      {Bullet point 1 about your Homelab setup or projects.}
%      \resumeItem{}
%      {Bullet point 2 about your Homelab setup or projects.}
%      % Add more bullet points as needed
%    \resumeItemListEnd
%\resumeSubHeadingListEnd
\end{document}


