%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{0.75in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://google.com/}{\Large Mershab Issadien}} & Email : \href{mailto:mershab99@gmail.com}{mershab99@gmail.com}\\
  \href& Mobile : +1-647-284-8025 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Ottawa}{Ottawa, ON}
      {Bsc. Honours Computer Science}{September 2017 - Current}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart



	\resumeSubheading
	{Praizl Inc.}{Richmond Hill, ON - Remote}
	{Full-Stack Software Engineer}{Jan 2021 - Present}
		\resumeItemListStart
			\resumeItem{REST API}
			{Developed a REST API using Python(Flask) and Java(Dropwizard). Built Resources for endpoints including User Management Resources for easy front-end communication}
			\resumeItem{Database}
			{Built MongoDB data schema + Java-Mongo communication library and developed Python data-stores. Built Mongo Caching layer which reduced latency/load time by 40\% Managed and maintained InfluxDB datastore}
			\resumeItem{Efficiency}
			{Developed asynchronous job scheduler in Python to reduce HTTP request latency 54\%}	
			\resumeItem{Analytics}
			{Developed Recommendation Engine for Real Estate Insights using InfluxDB time-series data, as well as manipulated datasets using mathematical algorithms}
			\resumeItem{Testing and Validation}
			{Tested and validated my own code. PR's were also subject to code review by senior engineers on every merge.}
			\resumeItem{Deployment}
			{Using Docker and Kubernetes, Deploying and maintaining containers with load balancing (.yaml configurations) }
			\resumeItem{Project Management}
			{Worked in Agile teams on a Feature-by-Feature basis using SCRUM organizational tools }
		\resumeItemListEnd
	    \resumeSubheading
	      {The Home Depot}{Richmond Hill, ON}
	      {Sales Associate/Inventory Associate}{May 2019 - August 2019}
	      \resumeItemListStart
	        \resumeItem{General}
	          {Developed teamwork skills as a sales associate, and learned the sales model of Home Depot through customer interaction.}
	        \resumeItem{System Feedback}
	          {Learned the inventory system (SAP powered) as well as provided bug feedback for the software development team. Improved efficiency by 12.5\% (1 Hour Day)}
		\resumeItem{Accomplishments}
		 {Sales Employee of the Month (July), 3x Homer Awards}     
\resumeItemListEnd

\resumeSubHeadingListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------





%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
	\resumeSubheading
	{Ryerson Climate Hack-To-Action Hackathon}{Toronto, ON}
	{Team Hackathon Competitor}{May 2016}
		\resumeItemListStart
			\resumeItem{General}
			{Developed a functional Android application with a SQL backend within 24 hours.}
			\resumeItem{Result}
			{3rd Place (\$1000 Prize)}
		\resumeItemListEnd
	\resumeSubheading
	{YRDSB QUEST 2016}{Richmond Hill, ON}
	{Engineering Team Lead}{May 2016}
		\resumeItemListStart
			\resumeItem{Leadership}
			{Lead a team of 3 tech/engineering students, performed requirement elicitation, communicated with other interdisciplinary teams and managed a project schedule to finish well within the timeline. }
			\resumeItem{Project Description}
			{Array of flowers that individually opened up based on proximity. Developed for mental health awareness.}
			\resumeItem{General}
			{Worked in interdisciplinary groups to create electronics backed art installations using Arduino and solenoids.}
		\resumeItemListEnd
%	\resumeSubheading
%	{YRDSB QUEST 2015}{Richmond Hill, ON}
%	{Engineering Team Lead}{May 2015}
%		\resumeItemListStart
%			\resumeItem{Leadership}
%			{Lead a team of 2 tech/engineering students and managed a project schedule to finish well within the timeline. }
%			\resumeItem{Project Description}
%			{Shevrons that when completed by a human circuit play sounds}
%			\resumeItem{General}
%			{Worked in interdisciplinary groups to create electronics backed art installations using Raspberry PI and Makey Makey's. .}
%		\resumeItemListEnd
  \resumeSubHeadingListEnd

%---------REFERENCES--------
\section{References}
	\resumeSubHeadingListStart
		\resumeSubheading
		{Ramie Raufdeen}{Praizl Project}
		{Senior Software Engineer at Salesforce}{}
			\resumeItemListStart
				\resumeSubItem{Relationship}
				{Ramie mentored me and supervised my work on the Praizl project.}
			\resumeItemListEnd
	\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
	\item{
	\textbf{Proficient}{: Java, Python, REST Frameworks (Flask, Dropwizard), Maven, MongoDB, SQL, Docker, Git version control, C\#, Arduino}
    	}
	\item{
		\textbf{Learning}{: Kubernetes, InfluxDB, PostgreSQL, Django, Node.js}
	}
  \resumeSubHeadingListEnd
%---------------------------------------------

%----------HOBBIES
\section{Hobbies}
	\resumeSubHeadingListStart
	\item{
	\textbf{}{Martial Arts, Fitness, Team Sports, Former Captain of Esports Team (DoTa 2), Fighting game enthusiast }
	}
	\resumeSubHeadingListEnd
\end{document}
